---
format: html
echo: false
warning: false
---

```{r}
library(surveydown)
```

::: {#basic_showif .sd-page}

# Demo survey of the `show_if` feature

::: {.callout-note}

This is a demo survey showcasing the functionality of <a href="https://surveydown.org" target="_blank">surveydown</a>. It doesn't collect any data.

The GitHub repo of this demo can be accessed <a href="https://github.com/surveydown-dev/demo-show-if" target="_blank">here</a>.

:::

## Simple Conditional Display

If the "**Other**" option is chosen, a question asking the other penguin type will appear.

This is done by using the `sd_show_if()` function in the `server` of `app.R`.

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins_simple',
  label = "Which is your favorite type of penguin?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo',
    'Other'     = 'other'
  )
)

sd_question(
  type  = "text",
  id    = "penguins_simple_other",
  label = "Please specify the other penguin type:"
)

sd_next()
```

:::

::: {#custom_showif .sd-page}

## Complex Conditional Display

Say that we want to have a more complicated `show_if` condition. Now there are 2 questions. Only if the user chooses both "**Other**" and "**Show**" will the other penguin question appear. This is also done by using the `sd_show_if()` function in the `server` of `app.R`.

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins_complex',
  label = "Which is your favorite type of penguin?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo',
    'Other'     = 'other'
  )
)

sd_question(
  type  = 'mc',
  id    = 'show_other',
  label = "Should we show the 'other' option question?",
  option = c(
    'Show' = 'show',
    'Hide' = 'hide'
  )
)

sd_question(
  type  = "text",
  id    = "penguins_complex_other",
  label = "Please specify the other penguin type:"
)

sd_next()
```

:::

::: {#end .sd-page}

## This is the end of the demo survey showcasing the conditional display feature.

```{r}
sd_close()
```

:::
